Sterile Neutrinos, a Summary

### 2015-04-15 p3_505/presentation/pres.tex
added the conclusion slide

\begin{frame}
  \frametitle{Conclusions}
  \begin{itemize}
  \item Sterile neutrinos\ldots
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Conclusions}
  \begin{itemize}
  \item A discovery of heavy, right-handed sterile neutrinos would have a large impact on our understanding of neutrino physics
  \item Some, very contested, evidence for sterile neutrinos has been found at LSND and MiniBooNE
  \item MINOS+, Super-K, Daya Bay, MicroBooNE, and NoVA will continue searching for sterile neutrinos
  \item Expect to see the anomalies be confirmed or refuted in the next year or two
  \end{itemize}
\end{frame}
